Sketch Recognition and Understanding

### 2009-07-28 trunk/draft/chapterSurvey.tex
save to version before defense
change i mad for pso1

   The next section describes in details the Particle Swarm Optimization and its advantages and disadvantages. 
% Kennedy and Eberhart \cite{PSOFirst,PSO2} introduced Particle Swarm Optimization Algorithm (PSO). The algorithm simulate the moving Kennedy and Eberhart \cite{PSOFirst,PSO2} introduced particle swarm algorithm (PSO) as a general optimization algorithm.  
 \subsection*{Particle Swarm Optimization}
 In optimization problems, the algorithm attempts to find a feasible solution which satisfies all constrain of this problem. An optimal solution is the best feasible solution in the solution space. Several methods were used to solve optimization problems. Stochastic search is based on the assumption that good solution are near each other. Algorithms like simulating annealing and hill climbing used stochastic to find best solution. The problem in these methods is they may be trapped into a local best and fail to find the global best solution.

@@

 PSO can be viewed as an algorithm between stochastic search and Evolutionary algorithms\cite{PSOpattern}. In general the PSO is a continuous optimization problem but experiments showed it performed as GA is discrete and binary optimization problems. The comparison between PSO and Genetic algorithm was performed in \cite{PSOGAComp} and proved that PSO generate faster, better solutions than GA especially in problems with high dimensionality.

@@

\subsection*{PSO Neighborhood Topology}  
In general the PSO algorithm have fully connected particle which means that every particle know the global best and local best of each other particle. Other forms of cooperation and organization were suggested in various systems.  \cite{grid} suggested using a grid like topology where particle are connected to four other particles around it. A ring and star topology were widely used in \cite{neighbourrhood}. The advantages over using different topology than the global best is that they slow down the swarm evolving (they need more time to propagate the best solution) which enable more space exploration and thus helps in eliminating the premature convergence problem. In \cite{hiericalPSO}, Janson and Middendorf proposed to use a dynamic and hierarchical neighborhood structure. They showed that using such structure helps in maintaining diversity over the solution space in a dynamic problem. % a PSO using a dynamic and hierarchical neighborhood structure to handle dynamic optimization problems. They demonstrated that such a structure is useful for maintaining some particle diversity in a dynamic environment.

@@

\subsection*{Drawbacks}

@@

\subsection*{Improvements to PSO}

@@

\subsection*{Particle Swarm Applications}
\label{sec:SwarmApp}

@@

\subsection*{Discrite Particle Swarm Equations(DPSO)}
%\section{Particle Swarm Algorithm}
%\label{PSO}
%What is particle swarm algorithm and how it was used in related researches. 
The main idea of \textit{Particle Swarm Algorithm (PSO)} is to represent each solution with a $N$ dimension particle from the solution space \cite{PSOFirst}. Each particle moves with a direction and velocity $v_{ij}$ based on equations \ref{eq:Swarm} \& \ref{eq:Swarm1}.
\begin{equation}
%\[
p_{ij}=p_{ij}+v_{ij},
%\
\label{eq:Swarm1}
\end{equation}
where $p_{ij}$ represent the $jth$ dimension in the $ith$ particle and $v_{ij}$ is the velocity of the $jth$ dimension in the $ith$ particle.
 %Equation [\ref{eq:Swarm}] shows how velocity and direction of each particle are computed
 \begin{equation}
v_{ij}  = v_{ij} W  + c_1 r_1 (lbest_{ij}  - p_{ij} ) + c_2 r_2 (gbest_{ij}  - p_{ij} )
\label{eq:Swarm}
\end{equation}
 where $W$ is the inertia weight parameter which controls the tradeoff between exploration and exploitation, $lbest_{ij}$ is the local best particle, $gbest_{ij}$ is the global best particle, $r_1$ \& $r_2$ are random variables and $c_1$ \& $c_2$ are the swarm acceleration parameters.
 After each iteration the global best $g_{best}$ particle and the agent local best $l_{best}$ particle are evaluated based on the maximum fitness functions of all particles in the solution space.

>>>>

   The next section describes in details the Particle Swarm Optimization and its advantages and disadvantages. 
% Kennedy and Eberhart \cite{PSOFirst,PSO2} introduced Particle Swarm Optimization Algorithm (PSO). The algorithm simulate the moving Kennedy and Eberhart \cite{PSOFirst,PSO2} introduced particle swarm algorithm (PSO) as a general optimization algorithm.  
 \subsection{Particle Swarm Optimization}
 In optimization problems, the algorithm attempts to find a feasible solution which satisfies all constrain of this problem. An optimal solution is the best feasible solution in the solution space. Several methods were used to solve optimization problems. Stochastic search is based on the assumption that good solution are near each other. Algorithms like simulating annealing and hill climbing used stochastic to find best solution. The problem in these methods is they may be trapped into a local best and fail to find the global best solution.

@@

\subsection{PSO vs. GA}
 PSO can be viewed as an algorithm between stochastic search and Evolutionary algorithms\cite{PSOpattern}. In general the PSO is a continuous optimization problem but experiments showed it performed as well as GA which is in general a discrete and binary optimization problem.

 The comparison between PSO and Genetic algorithm was performed in \cite{PSOGAComp} and proved that PSO generate faster, better optimal solutions than GA especially in problems with high dimensionality. In addition, Rohinsons et al. \cite{RohinsonPSGA} proved that PSO performed better than GA in difficult engineering problems \cite{EngineerProblemGA}.

% Eberhart \cite{PSOGAComp}

@@

 %From the procedure, we can learn that PSO shares many common points with GA. Both algorithms start with a group of a randomly generated population, both have fitness values to evaluate the population. Both update the population and search for the optimium with random techniques. Both systems do not guarantee success.

%However, PSO does not have genetic operators like crossover and mutation. Particles update themselves with the internal velocity. They also have memory, which is important to the algorithm.

%Compared with genetic algorithms (GAs), the information sharing mechanism in PSO is significantly different. In GAs, chromosomes share information with each other. So the whole population moves like a one group towards an optimal area. In PSO, only gBest (or lBest) gives out the information to others. It is a one -way information sharing mechanism. The evolution only looks for the best solution. Compared with GA, all the particles tend to converge to the best solution quickly even in the local version in most cases.

\subsection{PSO Neighborhood Topology}  
In general the PSO algorithm have fully connected particle which means that every particle know the global best and local best of each other particle. Other forms of cooperation and organization were suggested in various systems.  \cite{grid} suggested using a grid like topology where particle are connected to four other particles around it. A ring and star topology were widely used in \cite{neighbourrhood}. The advantages over using different topology than the global best is that they slow down the swarm evolving (they need more time to propagate the best solution) which enable more space exploration and thus helps in eliminating the premature convergence problem. In \cite{hiericalPSO}, Janson and Middendorf proposed to use a dynamic and hierarchical neighborhood structure. They showed that using such structure helps in maintaining diversity over the solution space in a dynamic problem. % a PSO using a dynamic and hierarchical neighborhood structure to handle dynamic optimization problems. They demonstrated that such a structure is useful for maintaining some particle diversity in a dynamic environment.

@@

%\subsection*{PSO vs. Genetic Algorithms}  
% compare   between genetic programming and algorihtms.

\subsection{Drawbacks}

@@

\subsection{Improvements to PSO}

@@

\subsection{Particle Swarm Applications}
\label{sec:SwarmApp}

@@

\subsection{Discrete Particle Swarm Equations(DPSO)}
%\section{Particle Swarm Algorithm}
%\label{PSO}
%What is particle swarm algorithm and how it was used in related researches. 
The main idea of \textit{Particle Swarm Algorithm (PSO)} is to represent each solution with a $N$ dimension particle from the solution space \cite{PSOFirst}. Each particle moves with a direction and velocity $v_{ij}$ based on equations \ref{eq:Swarm1} \& \ref{eq:Swarm}.
\begin{equation}
%\[
p_{ij}=p_{ij}+v_{ij},
%\
\label{eq:Swarm1}
\end{equation}
where $p_{ij}$ represent the $jth$ dimension in the $ith$ particle and $v_{ij}$ is the velocity of the $jth$ dimension in the $ith$ particle.
 %Equation [\ref{eq:Swarm}] shows how velocity and direction of each particle are computed
 \begin{equation}
v_{ij}  = v_{ij} W  + c_1 r_1 (lbest_{ij}  - p_{ij} ) + c_2 r_2 (gbest_{ij}  - p_{ij} )
\label{eq:Swarm}
\end{equation}
 where $W$ is the inertia weight parameter which controls the tradeoff between exploration and exploitation, $lbest_{ij}$ is the local best particle, $gbest_{ij}$ is the global best particle, $r_1$ \& $r_2$ are random variables and $c_1$ \& $c_2$ are the swarm acceleration parameters.
 After each iteration the global best $g_{best}$ particle and the agent local best $l_{best}$ particle are evaluated based on the maximum fitness functions of all particles in the solution space.
